\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-30 Manuscript/supp.tex
added section 3 back

% \section{Results from Data Excluding Positive Disqualified RTs}

% An earlier iteration of the paper fit a model that did not include RTs from
% athletes who were disqualified or did not finish but still registered a RT.  
% However, it was ultimately decided to include these times to better estimate the 
% left tail of the distribution and more accurately predict the probability of a 
% low RT, as described in the main paper.  
% We did not include negative RTs, however, as these represent a mistake 
% of the runner for starting before
% the gun is fired and are thus meaningless in our objective to
% determine a fair RT barrier.  Not all of those disqualified were
% disqualified because of breaking the 0.1 reaction time barrier; there are many
% reasons why an athlete may be disqualified, with the most notable being failed
% drug tests and lane violations.  Nonetheless, in this section,
% we exclude all disqualified RTs to see their effect on the probability of an
% extreme RT.  We fit an identical model to the generalized Gamma model
% presented in Section 3.2 to examine differences results.

% \begin{table}
%   \centering
%   \caption{Probabilities of observing RTs less than threshold 0.08,
%   0.09, and 0.10 seconds based on the
%     fitted GG GAMLSS model with both venue- and heat-level
% random effects.}
%   \begin{tabular}{c c c c}
%    \toprule
%    Data Set & Threshold 0.08 & Threshold 0.09 & Threshold 0.10  \\
%    \midrule
%    Without DQs & $4.93\cdot10^{-5}$ & $3.53\cdot10^{-4}$ &  $1.97\cdot10^{-3}$  \\
%    With DQs & $6.84\cdot10^{-5}$ & $4.95\cdot10^{-4}$ & $2.76\cdot10^{-3}$ \\
%    \bottomrule
%   \end{tabular}
%   \label{tab:DQSim_probability}
% \end{table}

% \jy{Men's data or pooled data?}
% \eds{with or without 2022?}
% \of{I dont know if we have time for this or if this fits the scope of what we
% are working on.}

% Table~\ref{tab:DQSim_probability} shows the effect of removing disqualificated
% times from the analysis.  The probability of observing extreme RTs is lower when
% we remove the 17 observations.

>>>>

\section{Results from Data Excluding Positive Disqualified RTs}

An earlier iteration of the paper fit a model that did not include RTs from
athletes who were disqualified or did not finish but still registered a RT.  
However, it was ultimately decided to include these times to better estimate the 
left tail of the distribution and more accurately predict the probability of a 
low RT, as described in the main paper.  We consider data from men's dash and
hurdles and include 2022 in our analysis to try and determine how sensitive
our model is to the inclusion of these times.

We did not include negative RTs, however, as these represent a mistake of the
runner for starting before the gun is fired and are thus meaningless in our
objective to determine a fair RT barrier.  Not all of those disqualified were
disqualified because of breaking the 0.1 reaction time barrier; there are many
reasons why an athlete may be disqualified, with the most notable being failed
drug tests and lane violations.  Nonetheless, in this section,
we exclude all disqualified RTs to see their effect on the probability of an
extreme RT.  We fit an identical model to the generalized Gamma model
presented in Section 3.2 to examine differences results.

\begin{table}
  \centering
   \caption{Probabilities of observing RTs less than threshold 0.08,
   0.09, and 0.10 seconds based on the
     fitted GG GAMLSS model with both venue- and heat-level
 random effects.}
   \begin{tabular}{c c c c}
    \toprule
    Data Set & Threshold 0.08 & Threshold 0.09 & Threshold 0.10  \\
    \midrule
    Without DQs & $4.93\cdot10^{-5}$ & $3.53\cdot10^{-4}$ &  $1.97\cdot10^{-3}$  \\
    With DQs & $6.84\cdot10^{-5}$ & $4.95\cdot10^{-4}$ & $2.76\cdot10^{-3}$ \\
    \bottomrule
   \end{tabular}
   \label{tab:DQSim_probability}
 \end{table}

Table~\ref{tab:DQSim_probability} shows the effect of removing disqualificated
times from the analysis.  The probability of observing extreme RTs is lower when
we remove the 17 observations.  While the probability of observing an extreme
reaction time is less when we remove disqualfied athletes, many of the same
conclusions remain the same: the current standards for disqualification are not
grounded in statistical analysis, and there appear to be unequal standards for men
and women.
